Validation failed EVT

### 2023-03-30 analysis/article-results.Rmd
rmd is part of targets pipeline, and 2nd test md

---
title: "Validation failed EVT"
author: "E. F. Bonneville"
date: "`r Sys.setenv(LANG = 'en_US.UTF-8'); format(Sys.Date(), '%d %B %Y')`"
output: 
  html_document:
    keep_md: true
    df_print: kable
    toc: yes
    toc_float: 
      smooth_scroll: false
editor_options: 
  chunk_output_type: console
---

@@

# Load libraries just for analysis rmd
library(ggplot2)
library(targets)
library(tidyverse)
library(tableone)
library(rms)
library(glmnet)
library(DT)
library(broom.helpers)
library(broom)
```

@@

#https://stackoverflow.com/questions/50039186/add-download-buttons-in-dtrenderdatatable
DT::datatable(
  tab_contin,
  extensions = 'Buttons',
  options = list(
    dom = 'Blfrtip', 
    buttons = c('csv', 'excel', 'pdf'),
    lengthMenu = list(c(10, 25, 50, -1), c(10, 25, 50, "All"))
  )
)
```

@@

DT::datatable(
  tab_cat,
  extensions = 'Buttons',
  options = list(
    dom = 'Blfrtip', 
    buttons = c('csv', 'excel', 'pdf'),
    lengthMenu = list(c(10, 25, 50, -1), c(10, 25, 50, "All"))
  )
)
```

@@

dat_to_impute |> 
  group_by(dataset) |> 
  naniar::miss_var_summary() |> 
  mutate(across(where(is.numeric), ~ round(.x, 2L))) |> 
  DT::datatable(
    extensions = 'Buttons',
    options = list(
      dom = 'Blfrtip', 
      buttons = c('csv', 'excel', 'pdf'),
      lengthMenu = list(c(10, 25, 50, -1), c(10, 25, 50, "All"))
    )
  )  
```

@@

# Print penalised model coefficients
#knitr::kable(data.frame(mod_coefs))
DT::datatable(
  data.frame(round(mod_coefs, digits = 3)),
  extensions = 'Buttons',
  options = list(
    dom = 'Blfrtip', 
    buttons = c('csv', 'excel', 'pdf'),
    lengthMenu = list(c(10, 25, 50, -1), c(10, 25, 50, "All"))
  )
)
```

@@

DT::datatable(
  summ_inter,
  extensions = 'Buttons',
  options = list(
    dom = 'Blfrtip', 
    buttons = c('csv', 'excel', 'pdf'),
    lengthMenu = list(c(10, 25, 50, -1), c(10, 25, 50, "All"))
  )
)
```

@@

cbind.data.frame(
  "Term" = dev_unpen$term, 
  "Development \n cohort" = dev_unpen$Development, 
  "Validation \n cohort" = valid_unpen$Validation,
  "Combined \n cohort" = comb_unpen$Combined
) |> 
  DT::datatable(
  extensions = 'Buttons',
  options = list(
    dom = 'Blfrtip', 
    buttons = c('csv', 'excel', 'pdf'),
    lengthMenu = list(c(10, 25, 50, -1), c(10, 25, 50, "All"))
  )
)
```

@@

# Print penalised model coefficients
DT::datatable(
  data.frame(round(mod_coefs_comb, digits = 3)),
  extensions = 'Buttons',
  options = list(
    dom = 'Blfrtip', 
    buttons = c('csv', 'excel', 'pdf'),
    lengthMenu = list(c(10, 25, 50, -1), c(10, 25, 50, "All"))
  )
)

@@

@@

dd <- datadist(dat_nomogram)
options(datadist = "dd")

>>>>

---
title: "Validation failed EVT"
author: "E. F. Bonneville"
date: "`r Sys.setenv(LANG = 'en_US.UTF-8'); format(Sys.Date(), '%d %B %Y')`"
output: 
  html_document:
    keep_md: true
    df_print: kable
    toc: yes
    toc_float: 
      smooth_scroll: false
editor_options: 
  chunk_output_type: console
params:
  interactive_tables: FALSE
---

@@

# Load libraries just for analysis rmd
library(ggplot2)
library(targets)
library(tidyverse)
library(tableone)
library(rms)
library(glmnet)
library(DT)
library(broom.helpers)
library(broom)
library(knitr)
```

@@

#https://stackoverflow.com/questions/50039186/add-download-buttons-in-dtrenderdatatable
if (params$interactive_tables) {
  DT::datatable(
    tab_contin,
    extensions = 'Buttons',
    options = list(
      dom = 'Blfrtip', 
      buttons = c('csv', 'excel', 'pdf'),
      lengthMenu = list(c(10, 25, 50, -1), c(10, 25, 50, "All"))
    )
  )
} else kableone(table_one$ContTable)

```

@@

if (params$interactive_tables) {
  DT::datatable(
    tab_cat,
    extensions = 'Buttons',
    options = list(
      dom = 'Blfrtip', 
      buttons = c('csv', 'excel', 'pdf'),
      lengthMenu = list(c(10, 25, 50, -1), c(10, 25, 50, "All"))
    )
  )
} else kableone(table_one$CatTable)
```

@@

df_missings <- dat_to_impute |> 
  group_by(dataset) |> 
  naniar::miss_var_summary() |> 
  mutate(across(where(is.numeric), ~ round(.x, 2L)))

if (params$interactive_tables)  {
  DT::datatable(
    df_missings,
    extensions = 'Buttons',
    options = list(
      dom = 'Blfrtip', 
      buttons = c('csv', 'excel', 'pdf'),
      lengthMenu = list(c(10, 25, 50, -1), c(10, 25, 50, "All"))
    )
  )  
} else kable(df_missings)
```

@@

# Print penalised model coefficients
#knitr::kable(data.frame(mod_coefs))

if (params$interactive_tables)  {

  DT::datatable(
    data.frame(round(mod_coefs, digits = 3)),
    extensions = 'Buttons',
    options = list(
      dom = 'Blfrtip', 
      buttons = c('csv', 'excel', 'pdf'),
      lengthMenu = list(c(10, 25, 50, -1), c(10, 25, 50, "All"))
    )
  )
} else kable(data.frame(round(mod_coefs, digits = 3)))
```

@@

if (params$interactive_tables) {
  DT::datatable(
    summ_inter,
    extensions = 'Buttons',
    options = list(
      dom = 'Blfrtip', 
      buttons = c('csv', 'excel', 'pdf'),
      lengthMenu = list(c(10, 25, 50, -1), c(10, 25, 50, "All"))
    )
  )
} else kable(summ_inter)
```

@@

df_unpen <- cbind.data.frame(
  "Term" = dev_unpen$term, 
  "Development cohort" = dev_unpen$Development, 
  "Validation cohort" = valid_unpen$Validation,
  "Combined cohort" = comb_unpen$Combined
)

if (params$interactive_tables) {
  DT::datatable(
    df_unpen,
    extensions = 'Buttons',
    options = list(
      dom = 'Blfrtip', 
      buttons = c('csv', 'excel', 'pdf'),
      lengthMenu = list(c(10, 25, 50, -1), c(10, 25, 50, "All"))
    )
  )
} else kable(df_unpen)
```

@@

# Print penalised model coefficients
if (params$interactive_tables) {
  DT::datatable(
    data.frame(round(mod_coefs_comb, digits = 3)),
    extensions = 'Buttons',
    options = list(
      dom = 'Blfrtip', 
      buttons = c('csv', 'excel', 'pdf'),
      lengthMenu = list(c(10, 25, 50, -1), c(10, 25, 50, "All"))
    )
  )
} else kable(data.frame(round(mod_coefs_comb, digits = 3)))

@@

dd <<- datadist(dat_nomogram)
options(datadist = "dd")

@@
